Collocated Deduplication with Fault Isolation for Virtual Machine Snapshot Backup

### 2013-07-11 snapshot_system/eval1.tex
cleaned up graph code, removed several obsolete figures

%graph comparing extreme binning (SRB) with CDS model (VC) for different cds percentages
\begin{figure}[ht]
  \centering
    \begin{tikzpicture}
            \begin{axis}[
            %title={Ex-Binning Efficiency},
            xlabel={Number of VMs added},
            ylabel={Dedup. Efficiency (\%)},
            %extra y ticks={4.5,5.5,6.5} %to add extra ticks
            mark options=solid,
            legend pos=south west,
            %legend columns=2,
            %legend style={
            %    at={(0.5,-0.2)},
            %anchor=north}
            ]
            \addplot[color=blue,mark=none] table[x=VMs,y=exbin] {figures/exbin_efficiency_comparison.txt};
            \addplot[densely dotted, color=red,mark=none] table[x=VMs,y=cds1] {figures/exbin_efficiency_comparison.txt};
            \addplot[loosely dotted, color=brown,mark=none] table[x=VMs,y=cds2] {figures/exbin_efficiency_comparison.txt};
            \addplot[densely dashed,color=black,mark=none] table[x=VMs,y=cds4] {figures/exbin_efficiency_comparison.txt};
            \legend{SRB,VC (1\%CDS),VC (2\%CDS),VC (4\%CDS)};
            \end{axis}
    \end{tikzpicture}
    \caption{Deduplication Efficiency
        ($efficiency=\frac{d-du}{d-du_{complete}}$) comparison between
    SRB and  VC.}
  \label{fig-exbin-efficiency-graph}
\end{figure}

>>>>

%graph comparing extreme binning (SRB) with CDS model (VC) for different cds percentages
\begin{figure}[ht]
  \centering
    \begin{tikzpicture}
            \begin{axis}[
            %title={Ex-Binning Efficiency},
            cycle list name=mline,
            xlabel={Number of VMs added},
            ylabel={Dedup. Efficiency (\%)},
            %extra y ticks={4.5,5.5,6.5} %to add extra ticks
            mark options=solid,
            legend pos=south west,
            %legend columns=2,
            %legend style={
            %    at={(0.5,-0.2)},
            %anchor=north},
            ]
            \addplot table[x=VMs,y=exbin] {figures/exbin_efficiency_comparison.txt};
            \addplot table[x=VMs,y=cds4] {figures/exbin_efficiency_comparison.txt};
            \addplot table[x=VMs,y=cds2] {figures/exbin_efficiency_comparison.txt};
            \addplot table[x=VMs,y=cds1] {figures/exbin_efficiency_comparison.txt};
            \legend{SRB,VC ($\sigma=4\%$),VC ($\sigma=2\%$),VC ($\sigma=1\%$)};
            \end{axis}
    \end{tikzpicture}
    \caption{Deduplication Efficiency
        ($efficiency=\frac{d-du}{d-du_{complete}}$) comparison between
    SRB and  VC.}
  \label{fig-exbin-efficiency-graph}
\end{figure}

### 2013-07-11 snapshot_system/failover.tex
cleaned up graph code, removed several obsolete figures

\comments{%dropping block links bec. we don't use it elsewhere
\begin{figure}[ht]
  \centering
  %\includegraphics[scale=.45,natwidth=511,natheight=276]{vo_links}
	\begin{tikzpicture}
		\begin{axis}[
		%title={VO Block links},
		xlabel={Number of VMs added},
		ylabel={Avg. links to a chunk},
		%extra y ticks={4.5,5.5,6.5} %because it only shows 4,5,6,7
		legend pos=south east
		]
		\addplot[color=blue,mark=*] table[x=VMs,y=Measured] {figures/vo_links.txt};
		\addplot[color=red,mark=square*] table[x=VMs,y=Theoretical] {figures/vo_links.txt};
		\legend{Measured,Theoretical};
		\end{axis}
	\end{tikzpicture}
  \caption{Average number of VMs sharing a data chunk in the global index}
  \label{fig-vo-links}
\end{figure}
}

\begin{figure}[ht]
  \centering
	\begin{tikzpicture}
		\begin{axis}[
		%title={VO FSB links},
		xlabel={Number of VMs},
		ylabel={\small Avg. Num. VMs sharing FSB},
		%extra y ticks={4.5,5.5,6.5} %to show extra ticks
		legend pos=north west
		]
                \addplot[color=blue,mark=*] table[x=VMs,y=FSBLinks] {figures/vo_fsb_links.txt};
		\addplot[color=red,mark=square*] table[x=VMs,y=cdslinks] {figures/cds_links.txt};
                \legend{VO, PDS in VC};
		\end{axis}
	\end{tikzpicture}
  \caption{Measured Average number of VMs sharing a 64MB FSB with global dedup (VO), and in a 2\% PDS for VC.}
  \label{fig-fsb-links}
\end{figure}

\begin{figure}[ht]
  \centering
	\begin{tikzpicture}
		\begin{axis}[
		%title={VO VM links},
		xlabel={Number of VMs},
		ylabel={\small Avg. Num. FSBs used by VM},
		%extra y ticks={4.5,5.5,6.5} %to show extra ticks
		legend pos=north west
		]
                \addplot[color=blue,mark=*] table[x=VMs,y=VMLinks] {figures/vo_vm_links.txt};
		\addplot[color=red,mark=square*] table[x=VMs,y=VMNonCDSLinks] {figures/vc_vm_links.txt};
		\addplot[color=red,densely dashed,mark=triangle*,mark size=3] table[x=VMs,y=VMCDSLinks] {figures/vc_vm_links.txt};
                \legend{$N_0$, $N_1$, $N_2$};
		\end{axis}
	\end{tikzpicture}
  \caption{Measured Average number of 64MB FSBs used by a single VM. For VC both the number of PDS and Non-PDS FSBs used are shown.}
  \label{fig-vm-links}
\end{figure}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%OLD MODEL START%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%The rate of increase in node failures can be seen in Figure~\ref{fig-vm-failure}
%(for a 100 node cluster).
%The graph assumes 10X40GB snapshots per VM with 18\% unique data after local
%dedup and 64MB filesytem chunks (which results in 1792 filesystem chunks per
%VM). We assume 18\% unique data after local dedup because that is what our
%snapshots have shown.

\comments{\begin{figure}[ht]
  \centering
  %\includegraphics[scale=.45,natwidth=511,natheight=276]{vo_links}
	\begin{tikzpicture}
		\begin{axis}[
		%title={Node failure affect on VMs},
		xlabel={Number of nodes failed},
		ylabel={\small chance that a VM is affected (\%) in VO},
		%extra y ticks={4.5,5.5,6.5} %because it only shows 4,5,6,7
		]
		\addplot[color=blue,mark=*] table{figures/vm_failure.txt};
		\end{axis}
	\end{tikzpicture}
  \caption{Percent chance that a VM is affected as storage nodes fail}
  \label{fig-vm-failure}
\end{figure}}

\comments{\begin{figure}[ht]
  \centering
  %\includegraphics[scale=.45,natwidth=511,natheight=276]{vo_links}
	\begin{tikzpicture}
		\begin{axis}[
		%title={Node failure affect on VMs},
		xlabel={Failed storage nodes},
		ylabel={\small Chance VM is affected (\%)},
		%extra y ticks={4.5,5.5,6.5} %if important numbers are missing
                mark options=solid,
                legend pos=north west
		]
                \addplot[densely dashed,color=blue,mark=*] table[x=NodesFailed,y=VO]{figures/vm_failure_1.txt};
                \addplot[color=red,mark=*] table[x=NodesFailed,y=VC1]{figures/vm_failure_1.txt};
                \addplot[color=red,mark=square*] table[x=NodesFailed,y=VC2]{figures/vm_failure_1.txt};
                \addplot[color=red,mark=triangle*,mark size=3] table[x=NodesFailed,y=VC3]{figures/vm_failure_1.txt};
                \legend{$VO$,$VC_{C_R=3}$,$VC_{C_R=4}$,$VC_{C_R=5}$,$VC_{C_R=6}$,$VC_{C_R=7}$}
		\end{axis}
	\end{tikzpicture}
  \caption{Percent chance that a VM is affected as storage nodes fail}
  \label{fig-vm-failure}
\end{figure}}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%OLD MODEL END%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%NEW MODEL START%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

\begin{figure}[ht]
  \centering
    \begin{tikzpicture}
            \begin{axis}[
            %title={FSB Availability},
            xlabel={Number of Machines Failed},
            ylabel={\small Availability of Single FSB (\%)},
            %extra y ticks={4.5,5.5,6.5} %to add extra ticks
            mark options=solid,
            legend pos=south west,
            %legend columns=2,
            %legend style={
            %    at={(0.5,-0.2)},
            %anchor=north}
            ]
            \addplot[color=blue,mark=none] table[x=NodesFailed,y=Availability5] {figures/fsb_availability.txt};
            \addplot[densely dashed, color=red,mark=none] table[x=NodesFailed,y=Availability4] {figures/fsb_availability.txt};
            \addplot[densely dotted,color=brown,mark=none] table[x=NodesFailed,y=Availability3] {figures/fsb_availability.txt};
            \legend{$R=5$,$R=4$,$R=3$};
            \end{axis}
    \end{tikzpicture}
    \caption{Availability of Individual FSBs in 100 Machine Cluster with different replication factors.}
  \label{fig-fsb-availability}
\end{figure}

\begin{figure}[ht]
  \centering
  %\includegraphics[scale=.45,natwidth=511,natheight=276]{vo_links}
	\begin{tikzpicture}
		\begin{axis}[
		%title={Node failure affect on VMs},
		xlabel={Failed storage nodes},
		ylabel={VM Snapshot Availability (\%)},
		extra y ticks={99.9}, %if important numbers are missing
                mark options=solid,
                legend style={
                    cells={anchor=west}, %legend entry alignment
                    legend pos=south west %legend position
                }
		]
                \addplot[densely dashed,color=blue,mark=square*] table[x=NodesFailed,y=VO2]{figures/vm_failure_2.txt};
                \addplot[densely dashed,color=blue,mark=*] table[x=NodesFailed,y=VO1]{figures/vm_failure_2.txt};
                %\addplot[densely dashed,color=blue,mark=triangle*,mark size=3] table[x=NodesFailed,y=VO3]{figures/vm_failure_2.txt};
                %\addplot[densely dashed,color=blue,mark=diamond*,mark size=3] table[x=NodesFailed,y=VO4]{figures/vm_failure_2.txt};
                \addplot[color=red,mark=square*] table[x=NodesFailed,y=VC2]{figures/vm_failure_2.txt};
                \addplot[color=red,mark=*] table[x=NodesFailed,y=VC1]{figures/vm_failure_2.txt};
                %\addplot[color=red,mark=triangle*,mark size=3] table[x=NodesFailed,y=VC3]{figures/vm_failure_2.txt};
                %\addplot[color=red,mark=diamond*,mark size=3] table[x=NodesFailed,y=VC4]{figures/vm_failure_2.txt};
            \legend{$VO\,10$ (optimistic),$VO\,5$ (measured),$VC\,1000$ (extreme),$VC\,20$ (measured)}
		\end{axis}
	\end{tikzpicture}
  \caption{Availability of VM backups as nodes fail for VO and VC models for varying degrees of block sharing (i.e. average number of VMs that use a block). Non-PDS replication fixed at 3 and PDS replication increased to 4.}
  \label{fig-vm-availability}
\end{figure}

\begin{figure}[ht]
  \centering
	\begin{tikzpicture}
		\begin{axis}[
		%title={PDS Replication affect on availability},
		xlabel={Failed storage nodes},
		ylabel={VM Snapshot Availability (\%)},
		extra y ticks={99.9}, %if important numbers are missing
                mark options=solid,
                legend style={
                    cells={anchor=west}, %legend entry alignment
                    legend pos=south west %legend position
                }
		]
                \addplot[color=blue,mark=*] table[x=NodesFailed,y=VC1]{figures/cds_replication.txt};
                \addplot[color=red,mark=square*] table[x=NodesFailed,y=VC2]{figures/cds_replication.txt};
                \addplot[color=brown,mark=triangle*,mark size=3] table[x=NodesFailed,y=VC3]{figures/cds_replication.txt};
                %\addplot[color=black,mark=diamond*,mark size=3] table[x=NodesFailed,y=VC4]{figures/cds_replication.txt};
                \legend{$R_C=3$,$R_C=4$,$R_C=5$}%,$R_C=7$}
		\end{axis}
	\end{tikzpicture}
  \caption{Availability of VM backups as nodes fail in the VC model for different PDS Replication factors (Non-PDS replication fixed at 3, and average PDS block links set to 1000)}
  \label{fig-pds-replication}
\end{figure}

\begin{figure}[ht]
  \centering
	\begin{tikzpicture}
		\begin{axis}[
		%title={PDS Replication affect on availability},
		xlabel={Failed storage nodes},
		ylabel={VM Snapshot Availability (\%)},
		extra y ticks={99.9}, %if important numbers are missing
                mark options=solid,
                legend style={
                    cells={anchor=west}, %legend entry alignment
                    legend pos=south west %legend position
                }
		]
                \addplot[color=blue,mark=*] table[x=NodesFailed,y=VC1]{figures/cds_replication2.txt};
                \addplot[color=red,mark=square*] table[x=NodesFailed,y=VC2]{figures/cds_replication2.txt};
                \addplot[color=brown,mark=triangle*,mark size=3] table[x=NodesFailed,y=VC3]{figures/cds_replication2.txt};
                %\addplot[color=black,mark=diamond*,mark size=3] table[x=NodesFailed,y=VC4]{figures/cds_replication2.txt};
                \legend{$R_C=3$,$R_C=4$,$R_C=5$}%,$R_C=7$}
		\end{axis}
	\end{tikzpicture}
  \caption{Availability of VM backups as nodes fail in the VC model for different PDS Replication factors (Non-PDS replication fixed at 3, and average PDS block links set to 20)}
  \label{fig-pds-replication2}
\end{figure}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%NEW MODEL END%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

>>>>

\comments{%dropping block links bec. we don't use it elsewhere
\begin{figure}[ht]
  \centering
  %\includegraphics[scale=.45,natwidth=511,natheight=276]{vo_links}
	\begin{tikzpicture}
		\begin{axis}[
		%title={VO Block links},
		xlabel={Number of VMs added},
		ylabel={Avg. links to a chunk},
		%extra y ticks={4.5,5.5,6.5} %because it only shows 4,5,6,7
		legend pos=south east
		]
		\addplot table[x=VMs,y=Measured] {figures/vo_links.txt};
		\addplot table[x=VMs,y=Theoretical] {figures/vo_links.txt};
		\legend{Measured,Theoretical};
		\end{axis}
	\end{tikzpicture}
  \caption{Average number of VMs sharing a data chunk in the global index}
  \label{fig-vo-links}
\end{figure}
}

\begin{figure}[ht]
  \centering
	\begin{tikzpicture}
		\begin{axis}[
		%title={VO FSB links},
		xlabel={Number of VMs},
		ylabel={\small Avg. Num. VMs sharing FSB},
		%extra y ticks={4.5,5.5,6.5} %to show extra ticks
		legend pos=north west
		]
                \addplot table[x=VMs,y=FSBLinks] {figures/vo_fsb_links.txt};
		\addplot table[x=VMs,y=cdslinks] {figures/cds_links.txt};
                \legend{VO, PDS in VC};
		\end{axis}
	\end{tikzpicture}
  \caption{Measured Average number of VMs sharing a 64MB FSB with global dedup (VO), and in a 2\% PDS for VC.}
  \label{fig-fsb-links}
\end{figure}

\begin{figure}[ht]
  \centering
	\begin{tikzpicture}
		\begin{axis}[
		%title={VO VM links},
		xlabel={Number of VMs},
		ylabel={\small Avg. Num. FSBs used by VM},
                ymin=0,
                mark options=solid,
		%extra y ticks={4.5,5.5,6.5} %to show extra ticks
		legend pos=north west
		]
                \addplot[color=blue,mark=*] table[x=VMs,y=VMLinks] {figures/vo_vm_links.txt};
		\addplot[color=red,mark=square*] table[x=VMs,y=VMNonCDSLinks] {figures/vc_vm_links.txt};
		\addplot[color=red,densely dashed,mark=triangle*,mark size=2.7] table[x=VMs,y=VMCDSLinks] {figures/vc_vm_links.txt};
                \legend{$N_0$, $N_1$, $N_2$};
		\end{axis}
	\end{tikzpicture}
  \caption{Measured Average number of 64MB FSBs used by a single VM. For VC both the number of PDS and Non-PDS FSBs used are shown.}
  \label{fig-vm-links}
\end{figure}

@@

@@

\begin{figure}[ht]
  \centering
    \begin{tikzpicture}
            \begin{axis}[
            %title={FSB Availability},
            cycle list name=mline,
            xlabel={Number of Machines Failed},
            ylabel={\small Availability of Single FSB (\%)},
            %extra y ticks={4.5,5.5,6.5} %to add extra ticks
            mark options=solid,
            legend pos=south west,
            %legend columns=2,
            %legend style={
            %    at={(0.5,-0.2)},
            %anchor=north}
            ]
            \addplot table[x=NodesFailed,y=Availability5] {figures/fsb_availability.txt};
            \addplot table[x=NodesFailed,y=Availability4] {figures/fsb_availability.txt};
            \addplot table[x=NodesFailed,y=Availability3] {figures/fsb_availability.txt};
            \legend{$R=5$,$R=4$,$R=3$};
            \end{axis}
    \end{tikzpicture}
    \caption{Availability of Individual FSBs in 100 Machine Cluster with different replication factors.}
  \label{fig-fsb-availability}
\end{figure}

\begin{figure}[ht]
  \centering
  %\includegraphics[scale=.45,natwidth=511,natheight=276]{vo_links}
	\begin{tikzpicture}
		\begin{axis}[
		%title={Node failure affect on VMs},
                cycle multi list={
                    mline\nextlist
                    [2 of]mmark*\nextlist
                },
		xlabel={Failed storage nodes},
		ylabel={VM Snapshot Availability (\%)},
		extra y ticks={99.9}, %if important numbers are missing
                mark options=solid,
                legend style={
                    cells={anchor=west}, %legend entry alignment
                    legend pos=south west %legend position
                },
                %reverse legend,
		]
                \addplot table[x=NodesFailed,y=VC1]{figures/vm_failure_2.txt};
                \addlegendentry{$VC\,20$ (measured)}
                \addplot table[x=NodesFailed,y=VC2]{figures/vm_failure_2.txt};
                \addlegendentry{$VC\,1000$ (extreme)}
                %\addplot table[x=NodesFailed,y=VC3]{figures/vm_failure_2.txt};
                %\addplot table[x=NodesFailed,y=VC4]{figures/vm_failure_2.txt};
                \addplot table[x=NodesFailed,y=VO1]{figures/vm_failure_2.txt};
                \addlegendentry{$VO\,5$ (measured)}
                \addplot table[x=NodesFailed,y=VO2]{figures/vm_failure_2.txt};
                \addlegendentry{$VO\,10$ (optimistic)}
                %\addplot table[x=NodesFailed,y=VO3]{figures/vm_failure_2.txt};
                %\addplot table[x=NodesFailed,y=VO4]{figures/vm_failure_2.txt};
		\end{axis}
	\end{tikzpicture}
  \caption{Availability of VM backups as nodes fail for VO and VC models for varying degrees of block sharing (i.e. average number of VMs that use a block). Non-PDS replication fixed at 3 and PDS replication increased to 4.}
  \label{fig-vm-availability}
\end{figure}

\begin{figure}[ht]
  \centering
	\begin{tikzpicture}
		\begin{axis}[
		%title={PDS Replication affect on availability},
		xlabel={Failed storage nodes},
		ylabel={VM Snapshot Availability (\%)},
		extra y ticks={99.9}, %if important numbers are missing
                mark options=solid,
                legend style={
                    cells={anchor=west}, %legend entry alignment
                    legend pos=south west %legend position
                },
                reverse legend,
		]
                \addplot table[x=NodesFailed,y=VC1]{figures/cds_replication.txt};
                \addplot table[x=NodesFailed,y=VC2]{figures/cds_replication.txt};
                \addplot table[x=NodesFailed,y=VC3]{figures/cds_replication.txt};
                %\addplot table[x=NodesFailed,y=VC4]{figures/cds_replication.txt};
                \legend{$R_C=3$,$R_C=4$,$R_C=5$}%,$R_C=7$}
		\end{axis}
	\end{tikzpicture}
  \caption{Availability of VM backups as nodes fail in the VC model for different PDS Replication factors (Non-PDS replication fixed at 3, and average PDS block links set to 1000)}
  \label{fig-pds-replication}
\end{figure}

\begin{figure}[ht]
  \centering
	\begin{tikzpicture}
		\begin{axis}[
		%title={PDS Replication affect on availability},
		xlabel={Failed storage nodes},
		ylabel={VM Snapshot Availability (\%)},
		extra y ticks={99.9}, %if important numbers are missing
                mark options=solid,
                legend style={
                    cells={anchor=west}, %legend entry alignment
                    legend pos=south west %legend position
                },
                reverse legend,
		]
                \addplot table[x=NodesFailed,y=VC1]{figures/cds_replication2.txt};
                \addplot table[x=NodesFailed,y=VC2]{figures/cds_replication2.txt};
                \addplot table[x=NodesFailed,y=VC3]{figures/cds_replication2.txt};
                %\addplot table[x=NodesFailed,y=VC4]{figures/cds_replication2.txt};
                \legend{$R_C=3$,$R_C=4$,$R_C=5$}%,$R_C=7$}
		\end{axis}
	\end{tikzpicture}
  \caption{Availability of VM backups as nodes fail in the VC model for different PDS Replication factors (Non-PDS replication fixed at 3, and average PDS block links set to 20)}
  \label{fig-pds-replication2}
\end{figure}

### 2013-07-11 snapshot_system/main.tex
change
w
modif
added plot for VO block links. still has some issue though.
Added CDS coverage graph with measured vs predicted. Not sure the predicted is helpful to the graph though.
Added VM failure figures for two different models
adding exper.
modify all sections
revise
update graphs
my local changes
update
removed extensions from pdf includes, set default ext in main updated makefile to include all proper prereqs, added phony remake and bibtex targets.
cleaned up graph code, removed several obsolete figures

\documentclass{acm_proc_article-sp}
\usepackage[colorlinks,linkcolor=red,anchorcolor=blue,citecolor=green,urlcolor=black]{hyperref}
\usepackage{epsfig}
\usepackage{breqn}

\newcommand{\comments}[1]{}

@@

\input{intro}
%\input{design}
\input{background}
\input{challenge}
\input{snapshot}
\input{failover}
\input{design1}
%\input{snapshot}
%\input{append}\
\input{cds}
%\input{delete}
%\input{failover}
\input{result}
\input{con}

>>>>

\documentclass{sig-alternate-10pt}
\usepackage{mathptmx}
\usepackage[colorlinks,linkcolor=red,anchorcolor=blue,citecolor=green,urlcolor=black]{hyperref}
\usepackage{subfigure}
\usepackage{epsfig}
\usepackage{multirow}
\usepackage{array}
\usepackage{breqn}
\usepackage{pgfplots}
\pgfplotsset{compat=1.7}
\DeclareGraphicsExtensions{.pdf}

\newcommand{\comments}[1]{}
%pgfplots setup
\pgfplotsset{every axis/.append style={
	very thick,
	tick style={thick}}}
\pgfplotsset{
        every mark/.append style={solid}
}
\pgfplotscreateplotcyclelist{mcolor}{%
    {blue,every mark/.append style={fill=blue},mark=*},
    {red,every mark/.append style={fill=red},mark=square*},
    {brown,every mark/.append style={fill=brown},mark=triangle*,mark size=3},
    {black,every mark/.append style={fill=black},mark=diamond*,mark size=3},
    {green!60!black,every mark/.append style={fill=green!60!black},mark=pentagon*,mark size=2.5},
    {magenta!90!black,every mark/.append style={fill=magenta!90!black},mark=star,mark size=3},
    {densely dashed,blue,every mark/.append style={fill=blue},mark=*},
    {densely dashed,red,every mark/.append style={fill=red},mark=square*},
    {densely dashed,brown,every mark/.append style={fill=brown},mark=triangle*,mark size=2.7},
    {densely dashed,black,every mark/.append style={fill=black},mark=diamond*,mark size=2.7},
    {densely dashed,green!60!black,every mark/.append style={fill=green!60!black},mark=pentagon*,mark size=2.5},
    {densely dashed,magenta!90!black,every mark/.append style={fill=magenta!90!black},mark=star,mark size=3}}

\pgfplotscreateplotcyclelist{mmark*}{
    {mark=*},
    {mark=square*},
    {mark=triangle*,mark size=2.7},
    {mark=diamond*,mark size=2.7},
    {mark=pentagon*,mark size=2.5},
    {mark=star,mark size=3},
    {mark=asterisk,mark size=3},
    {mark=+,mark size=3},
    {mark=Mercedes star,mark size=3}}

\pgfplotscreateplotcyclelist{mline}{
    {solid,blue,every mark/.append style={fill=blue}},
    {densely dashed,red,every mark/.append style={fill=red}},
    {densely dotted,brown,every mark/.append style={fill=brown}},
    {loosely dotted,black,every mark/.append style={fill=black}},
    {loosely dashed,green!60!black,every mark/.append style={fill=green!60!black}},
    {densely dashdotted,magenta!90!black,every mark/.append style={fill=magenta!90!black}},
    {densely dashdotdotted,teal,every mark/.append style={fill=teal}},
    {loosely dashdotted,orange,every mark/.append style={fill=orange}},
    {loosely dashdotdotted,violet,every mark/.append style={fill=violet}}}

    \pgfplotsset{cycle list name=mcolor}

@@

\input{intro}
%\input{design}
\input{background}
\input{challenge}
\input{snapshot}
\input{failover}
%\input{compare}
%\input{design1}
\input{arch}
%\input{impl}
%\input{sampling-comparison.txt}
\input{eval1}
%\input{cds}
%\input{delete}
%\input{failover}
%\input{result}
\input{con}

### 2013-07-11 snapshot_system/result.tex
cleaned up graph code, removed several obsolete figures

%graph comparing extreme binning (SRB) with CDS model (VC) for different cds percentages
\begin{figure}[ht]
  \centering
    \begin{tikzpicture}
            \begin{axis}[
            %title={Ex-Binning Efficiency},
            xlabel={Number of VMs added},
            ylabel={Dedup. Efficiency (\%)},
            %extra y ticks={4.5,5.5,6.5} %to add extra ticks
            mark options=solid,
            legend pos=south west,
            %legend columns=2,
            %legend style={
            %    at={(0.5,-0.2)},
            %anchor=north}
            ]
            \addplot[color=blue,mark=none] table[x=VMs,y=exbin] {figures/exbin_efficiency_comparison.txt};
            \addplot[densely dotted, color=red,mark=none] table[x=VMs,y=cds1] {figures/exbin_efficiency_comparison.txt};
            \addplot[loosely dotted, color=brown,mark=none] table[x=VMs,y=cds2] {figures/exbin_efficiency_comparison.txt};
            \addplot[densely dashed,color=black,mark=none] table[x=VMs,y=cds4] {figures/exbin_efficiency_comparison.txt};
            \legend{SRB,VC (1\%CDS),VC (2\%CDS),VC (4\%CDS)};
            \end{axis}
    \end{tikzpicture}
    \caption{Deduplication Efficiency
        ($efficiency=\frac{d-du}{d-du_{complete}}$) comparison between
    Stateless Routing with Binning and VC.}
  \label{fig-exbin-efficiency-graph}
\end{figure}

>>>>

%graph comparing extreme binning (SRB) with CDS model (VC) for different cds percentages
\begin{figure}[ht]
  \centering
    \begin{tikzpicture}
            \begin{axis}[
            %title={Ex-Binning Efficiency},
            cycle list name=mline,
            xlabel={Number of VMs added},
            ylabel={Dedup. Efficiency (\%)},
            %extra y ticks={4.5,5.5,6.5} %to add extra ticks
            mark options=solid,
            legend pos=south west,
            %legend columns=2,
            %legend style={
            %    at={(0.5,-0.2)},
            %anchor=north},
            ]
            \addplot table[x=VMs,y=exbin] {figures/exbin_efficiency_comparison.txt};
            \addplot table[x=VMs,y=cds4] {figures/exbin_efficiency_comparison.txt};
            \addplot table[x=VMs,y=cds2] {figures/exbin_efficiency_comparison.txt};
            \addplot table[x=VMs,y=cds1] {figures/exbin_efficiency_comparison.txt};
            \legend{SRB,VC ($\sigma=4\%$),VC ($\sigma=2\%$),VC ($\sigma=1\%$)};
            \end{axis}
    \end{tikzpicture}
    \caption{Deduplication Efficiency
        ($efficiency=\frac{d-du}{d-du_{complete}}$) comparison between
    Stateless Routing with Binning and VC.}
  \label{fig-exbin-efficiency-graph}
\end{figure}

### 2013-07-11 snapshot_system/snapshot.tex
CDS->PDS fix
cleaned up graph code, removed several obsolete figures

\begin{figure}[ht]
  \centering
    \begin{tikzpicture}
            \begin{axis}[
            %title={CDS Coverage},
            xlabel={Total number of chunks stored},
            ylabel={PDS Coverage (\%)},
            %extra y ticks={4.5,5.5,6.5} %to add extra ticks
            mark options=solid,
            %legend pos=outer north east,
            legend columns=2,
            legend style={
                at={(0.5,-0.2)},
            anchor=north}
            ]
            \addplot[color=blue,mark=*] table[x=InputChunks,y=A1] {figures/cds_coverage.txt};
            \addplot[color=blue,mark=square*] table[x=InputChunks,y=A2] {figures/cds_coverage.txt};
            \addplot[color=blue,mark=triangle*,mark size=3] table[x=InputChunks,y=A4] {figures/cds_coverage.txt};
            \addplot[densely dashed,color=red,mark=*] table[x=InputChunks,y=T1] {figures/cds_coverage.txt};
            \addplot[densely dashed,color=red,mark=square*] table[x=InputChunks,y=T2] {figures/cds_coverage.txt};
            \addplot[densely dashed,color=red,mark=triangle*] table[x=InputChunks,y=T4] {figures/cds_coverage.txt};
            \legend{Measured ($\sigma=1\%$),Measured ($\sigma=2\%$),Measured ($\sigma=4\%$),Predicted ($\sigma=1\%$),Predicted ($\sigma=2\%$),Predicted ($\sigma=4\%$)};
            \end{axis}
    \end{tikzpicture}
  \caption{fixed-alpha predicted vs. actual CDS coverage as data size increases.}
  \label{fig-cds-coverage}
\end{figure}

>>>>

\begin{figure}[ht]
  \centering
    \begin{tikzpicture}
            \begin{axis}[
            %title={PDS Coverage},
            %width=\columnwidth,
            cycle multi list={
                mline\nextlist
                [3 of]mmark*\nextlist
            },
            %cycle list name=mcolor,
            xlabel={Total num. chunks stored (in billions)},
            ylabel={PDS Coverage (\%)},
            %extra y ticks={4.5,5.5,6.5} %to add extra ticks
            mark options=solid,
            %legend pos=outer north east,
            legend columns=2,
            legend style={
                at={(0.5,-0.2)},
            anchor=north},
            ]
            \addplot table[x expr=\thisrow{InputChunks}/1000000000,y=A1] {figures/cds_coverage.txt};
            \addplot table[x expr=\thisrow{InputChunks}/1000000000,y=A2] {figures/cds_coverage.txt};
            \addplot table[x expr=\thisrow{InputChunks}/1000000000,y=A4] {figures/cds_coverage.txt};
            \addplot table[x expr=\thisrow{InputChunks}/1000000000,y=T1] {figures/cds_coverage.txt};
            \addplot table[x expr=\thisrow{InputChunks}/1000000000,y=T2] {figures/cds_coverage.txt};
            \addplot table[x expr=\thisrow{InputChunks}/1000000000,y=T4] {figures/cds_coverage.txt};
            \legend{Measured ($\sigma=1\%$),Measured ($\sigma=2\%$),Measured ($\sigma=4\%$),Predicted ($\sigma=1\%$),Predicted ($\sigma=2\%$),Predicted ($\sigma=4\%$)};
            \end{axis}
    \end{tikzpicture}
  \caption{fixed-alpha predicted vs. actual PDS coverage as data size increases.}
  \label{fig-cds-coverage}
\end{figure}
